Large Language Models in Reinforcement Learning - A Comparison of Methods

### 2023-10-03 doc/paper.tex
fix typos

\author{\IEEEauthorblockN{Adrian Duric}
\IEEEauthorblockA{\textit{Master Student, Dept. of Informatics} \\
\textit{The Faculty of Mathematics}\\
Oslo, Norway \\
adriandu@ifi.uio.no}
\and
\IEEEauthorblockN{Gregor Kajda}
\IEEEauthorblockA{\textit{Master Student, Dept. of Informatics} \\
\textit{The Faculty of Mathematics}\\
Oslo, Norway \\
grzegork@ifi.uio.no}
\and
\IEEEauthorblockN{Jonatan Hoffmann Hanssen}
\IEEEauthorblockA{\textit{Master Student, Dept. of Informatics} \\
\textit{The Faculty of Mathematics}\\
Oslo, Norway \\
jonatahh@ifi.uio.no}
}

>>>>

\author{\IEEEauthorblockN{Adrian Duric}
\IEEEauthorblockA{\textit{Master Student, Dept. of Informatics} \\
\textit{The Faculty of Mathematics}\\
\textit{and Natural Sciences}\\
Oslo, Norway \\
adriandu@ifi.uio.no}
\and
\IEEEauthorblockN{Gregor Kajda}
\IEEEauthorblockA{\textit{Master Student, Dept. of Informatics} \\
\textit{The Faculty of Mathematics}\\
\textit{and Natural Sciences}\\
Oslo, Norway \\
grzegork@ifi.uio.no}
\and
\IEEEauthorblockN{Jonatan Hoffmann Hanssen}
\IEEEauthorblockA{\textit{Master Student, Dept. of Informatics} \\
\textit{The Faculty of Mathematics}\\
\textit{and Natural Sciences}\\
Oslo, Norway \\
jonatahh@ifi.uio.no}
}
